Exp1 - Opt w_max and {A,phi)

### 2018-04-04 voltagebudget/analysis/paper_figures.Rmd
Added control exps
Hetero vis still in progress

# --------------------------------------------------------------------
# Summarize over As 
fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig2

@@

rm(df, exp, freq, freqs, name, ref, n)
```

@@

```{r, fig.width=2.7, fig.height=2.2}
fig1 %>% 
  group_by(N) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig1, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2

@@

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 24, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=.5, alpha=0.9, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  facet_wrap(~rank, nrow=3) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),s
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3

@@

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(y=V_osc/V_comp, x=factor(delta_spikes), group=delta_spikes)) +
  geom_jitter(aes(color=factor(delta_spikes)), size=0.01, alpha=0.1, width=0.2) +
  geom_boxplot(outlier.colour = NA, alpha=0.9, width=0.2) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  theme(legend.position = "none") +
  labs(y=expression(V[o]/V[c]), x="Spike count") + 
  coord_flip()  -> p4

@@

# Freq effects - var reduction versus additional 'sampling'?

```{r, fig.width=1.8, fig.height=2.25}
# ------------------------------------------
# SLOW
fig2 %>% 
  filter(freq <= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Avg. error (ms)") +
  scale_color_gradient2(
    low="gold", high="darkgreen", mid="darkgrey", 
    midpoint=20, name="Freq (Hz)", breaks = c(5, 10, 15, 20), limits=c(5, 20)) +
  theme_classic() +
  geom_vline(xintercept = 1, alpha=0.5, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.3, color="black", linetype="dashed") +
  scale_y_continuous(breaks=c(0, 4.0, 8.0, 12.0), limits=c(0, 12)) +
  theme(legend.position="top", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(freq <= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Pop. variance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  scale_y_continuous(breaks=c(8.0, 10, 12.0), limits=c(8, 12)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

fig2 %>% 
  filter(freq <= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  # labs(x=expression(V[o]/V[c]), y="Variance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  lims(y=c(9,11)) +
  theme_classic() +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      # axis.text.y=element_blank(),
      axis.ticks.x=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p2.sub

fig2 %>% 
  filter(freq <= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Spike count") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

# ------------------------------------------
# FAST
fig2 %>% 
  filter(freq >= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Avg. error (ms)") +
  scale_color_gradient2(
    low="gold", high="darkgreen", mid="darkgrey", 
    midpoint=20, name="", breaks = c(20, 25, 30)) +
  theme_classic() +
  geom_vline(xintercept = 1, alpha=0.5, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.3, color="black", linetype="dashed") +
  scale_y_continuous(breaks=c(0, 4.0, 8.0, 12.0), limits=c(0, 12)) +
  theme(legend.position="top", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p4

fig2 %>% 
  filter(freq >= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Pop. variance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  scale_y_continuous(breaks=c(8.0, 10, 12.0), limits=c(8, 12)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p5

fig2 %>%
  filter(freq >= 20) %>%
  filter(V_osc/V_comp <= 3) %>%
  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) +
  labs(x=expression(V[o]/V[c]), y="Spike count") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
  theme_classic() +
  theme(legend.position="none",
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p6

plot_grid <- rbind(
  c(1, 4),
  c(1, 4),
  c(1, 4),
  c(2, 5),
  c(2, 5),
  c(3, 6),
  c(3, 6))
grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, p5, p6, plot_grid)
```

>>>>

# Summarize over As 
fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig2

@@

# --------------------------------------------------------------------
# Load noise exp data...
# Osc
freq <- "20"

# sigma scan
exp <- "97"

sigmas <- c("1.0e-9", "2.0e-9", "3.0e-9", "4.0e-9", "5.0e-9")

fig8 <- NULL
for(sigma in sigmas){
  name <- paste("../data/exp", exp, "_sigma", sigma, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))

  df$sigma <- rep(as.numeric(sigma), nrow(df))
  fig8 <- rbind(fig8, df)
}

exp <- "96"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$sigma <- rep(0, nrow(df))
fig8 <- rbind(df, fig8)

# Process
fig8 %>% 
  filter(n_spikes_ref > 0) %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) -> fig8

# Summarize over As 
fig8 %>% 
  group_by(As, sigma) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig9

# --------------------------------------------------------------------
# Load weight exps
# Osc
freq <- "20"

# Init
fig10 <- NULL

# high w
exp <- "100"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$weight <- rep(2.48e-08, nrow(df))
fig10 <- rbind(df, fig10)

# Ref (Z=0)
exp <- "96"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$weight <- rep(8.25e-09, nrow(df))
fig10 <- rbind(df, fig10)

# low w
exp <- "99"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$weight <- rep(1.65e-09, nrow(df))
fig10 <- rbind(df, fig10)

# Process
fig10 %>% 
  filter(n_spikes_ref > 0) %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) -> fig10

# Summarize over As 
fig10 %>% 
  group_by(As, weight) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig11

# --------------------------------------------------------------------
# Hetero cells
# Osc
freq <- "20"

# Init
fig12 <- NULL

# high w
exp <- "101"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$weight <- rep(2.48e-08, nrow(df))
fig12 <- rbind(df, fig12)

# Process
fig12 %>% 
  filter(n_spikes_ref > 0) %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) -> fig12

# Summarize over As 
fig12 %>% 
  group_by(As, weight) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig13

# --------------------------------------------------------------------
rm(df, exp, freq, freqs, name, ref, n, sigmas, sigma, exps, alg_names, algs)
```

@@

```{r, fig.width=2.7, fig.height=2.2}
fig1 %>% 
  group_by(N) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig1, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2

@@

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 24, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=.5, alpha=0.9, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  facet_wrap(~rank, nrow=3) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),s
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3

@@

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(y=V_osc/V_comp, x=factor(delta_spikes), group=delta_spikes)) +
  geom_jitter(aes(color=factor(delta_spikes)), size=0.01, alpha=0.1, width=0.2) +
  geom_boxplot(outlier.colour = NA, alpha=0.9, width=0.2) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  geom_hline(yintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  theme(legend.position = "none") +
  labs(y=expression(V[o]/V[c]), x="Spike count") + 
  coord_flip()  -> p4

@@

# Control exps
## Freqs, noise, weight

```{r, fig.width=2.1, fig.height=2.4}
# --------------------------------------------------------------
# Freq
fig2 %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  group_by(N, freq) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Norm. error") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  group_by(N, freq) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

# --------------------------------------------------------------
# Noise
fig9 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, sigma) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=10e-3*(sigma/10e-9) * 1e3/2, group=interaction(N, sigma))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. error") +
  scale_color_gradient(low="grey", high="orange") +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

fig9 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, sigma) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=10e-3*(sigma/10e-9) * 1e3 /2, group=interaction(N, sigma))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
  scale_color_gradient(low="grey", high="orange", name="Noise (mV)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p4

# --------------------------------------------------------------
# Weight
fig11 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, weight) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=weight*1e9, group=interaction(N, weight))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. error") +
  scale_color_gradient2(
    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p5

fig11 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, weight) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=weight*1e9, group=interaction(N, weight))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
  scale_color_gradient2(
    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9, name="Weight (nS)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p6

plot_grid <- rbind(
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(3, 3, 3, 4, 4, 4, 4, 4),
  c(5, 5, 5, 6, 6, 6, 6, 6))

grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid)
```
## Heterocells
```{r, fig.width=1.1, fig.height=1.5}
fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_errors = errors/max(errors)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors/max(errors)), 
            color="black", size=0.8) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[b]), y="Norm. error") -> p1

fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_variances = variances/max(variances)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=variances/max(variances)), 
            color="black", size=0.8) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[b]), y="Norm. variance") -> p2

plot_grid <- rbind(
  c(1),
  c(2))
